\chapter{Bibliographie}

[1]Hermann Borotschnig, Lucas Paletta,Manfred Prantl and Axel Pinz 
Active Object Recognition in Parametric Eigenspace 
Submitted to BMVC98, Southampton, United Kingdom, 14-17 Sept. 1998 \\

[2] View-based dynamic object recognition based on human perception \\

[3] L.-C. Caron, D. Filliat, A. Gepperth.
Neural Network Fusion of Color, Depth and Location for Object Instance Recognition on a Mobile Robot. 
Second Workshop on Assistive Computer Vision and Robotics (ACVR), in conjunction with European Conference on Computer Vision, Sep 2014, Zurich, Switzerland.\\

[4] Radu Bogdan Rusu, Gary Bradski, Romain Thibaux, John Hsu,
Fast 3D Recognition and Pose Using the Viewpoint Feature Histogram \\

[5] G. Burel and H. Henocq
Three-dimensional invariants and their application to object recognition
Signal Process., vol. 45, no. 1, pp.1–22, 1995. \\

[6] A. Johnson and M. Hebert
Using spin images for efficient object recognition in cluttered 3D scenes
IEEE Transactions on Pattern Analysis and Machine Intelligence, May 1999. \\

[7] T. Gatzke, C. Grimm, M. Garland, and S. Zelinka 
Curvature Maps for Local Shape Comparison,” 
in SMI ’05: Proceedings of the International Conference on Shape Modeling and Applications 2005 (SMI’05), 2005, pp. 246–255. \\

[8] R. B. Rusu, N. Blodow, and M. Beetz, “Fast Point Feature Histograms
(FPFH) for 3D Registration,” in ICRA, 2009. \\

[9] B.-C. M. and G. C., “Characterizing shape using conformal factors,”
in Eurographics Workshop on 3D Object Retrieval, 2008. \\

[10] K. Lai, L., X. Ren, \& D. Fox  A Large-Scale Hierarchical Multi-View RGB-D Object Dataset In IEEE International Conference on Robotics and Automation (ICRA), May 2011. \\

[11] R. B. Rusu and S. Cousins, “3D is here: Point Cloud Library (PCL),”
in Proc. IEEE Int. Conf. Robotics and Automation (ICRA), Shanghai,
China, May 9–13, 2011, pp. 1–4. \\

[12] Three Dimensional object recognition and 6 dof pose estimation \\ 

[13] Bj\"{o}rn Browatzki, Vadim Tikhanoff, Giorgio Metta, Heinrich H. B\"{u}lthoff and Christian Wallraven 
Active Object Recognition on a Humanoid Robot
2012 IEEE International Conference on Robotics and Automation RiverCentre, Saint Paul, Minnesota, USA May 14-18, 2012 \\

[14] Roy, S., S. Chaudhury, and S. Banerjee: 2004, 
Active recognition through next view planning: a survey
Pattern Recognition 37(3), 429–446. \\

[15] Sumantra Dutta Roy, Santanu Chaudhury, and Subhashis Banerjee Abstract—In
Isolated 3-D Object Recognition through Next View Planning
IEEE TRANSACTIONS ON SYSTEMS, MAN, AND CYBERNETICS—PART A: SYSTEMS AND HUMANS, VOL. 30, NO. 1, JANUARY 2000 Correspondence. 67 \\

[16] Siddhartha S. Srinivasa Abstract—We
Efficient Multi-View Object Recognition and Full Pose Estimation Alvaro Collet
Published In Proceedings of the IEEE International Conference on Robotics and Automation (ICRA) , 2050-2055.\\

[17] Kristoffer Sjo, Dorian G\"{a}lvez López, C
Object Search and Localization for an Indoor Mobile Robot
Journal of Computing and Information Technology \\ %- CIT 17, 2009, 1, 67–80 doi:10.2498/cit.100118267

\textbf{Sites internet}

\url{http://pointclouds.org/documentation/tutorials/fpfh_estimation.php} \\

\url{https://github.com/PointCloudLibrary/pcl/wiki/Overview-and-Comparison-of-Features} \\

\url{http://www.pointclouds.org/documentation/tutorials/vfh_recognition.php#vfh-recognition} \\

\url{http://robotica.unileon.es/mediawiki/index.php/PCL/OpenNI\_tutorial\_4:\_3D\_object\_recognition\_(descriptors)}

